---
title: "DATA TAMING ASSIGNMENT 1"
author: "VINEETH MARIKUNTEMATHA RAVISHARADHYA-a1896845"
date: "23/02/2024"
output:
  pdf_document: default
  word_document: default
  html_document:
    
    df_print: paged
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

```{r }
#Load the required packages
library(here)
library(tidyverse)
library(tidyr)
library(stringr)
library(forcats)
library(lubridate)
library(inspectdf)
library(ggplot2)
```

# Q1. Loading the data

```{r}
# Your student number goes here
ysn = 1896845
# Calculate your student number modulo 3
filenum <- ysn %% 3
filenum
filename <- paste0("D:/r studio files/Assignment_1/archery_2.csv")
filename

# Read in the data
archery_2 <- read_csv("archery_2.csv")
# Display the first 10 lines of the data

archery_2
```

```{r}
print(n=10,archery_2)
```


# Q2. Taking a random sample of archers

```{r}
set.seed(1896845)
sample_archery_2 <- sample_n(archery_2, 100)

sample_archery_2
```


# Q3. Tidying the data

## Q3(a). Converting from wide form to long form
```{r}
library(tidyr)

archery_wide_long <- gather(sample_archery_2, key = "session", value = "result", session_1:session_6)
sample_archery_2

```

## Q3(b). Replacing `result` with 2 new columns
```{r}
sample <- str_match(archery_wide_long$result,"Target hit (\\d+) times from (\\d+) shots")
archery_wide_long <- mutate(archery_wide_long,result = NULL)
archery_wide_long <-mutate(archery_wide_long,
shots = sample[,3],
hits = sample[,2]
)
archery_wide_long



archery_wide_long


```

## Q3(c). Replace data in `session` column with session number
```{r}


trial <- str_match(archery_wide_long$session, "session_(\\d+)")


archery_wide_long <- mutate(archery_wide_long,
                            session = as.integer(trial[, 2]))


archery_wide_long

```

## Q3(d). Replace "Yes/No" with "TRUE/FALSE"
```{r}
archery_wide_long$experienced[archery_wide_long$experienced == "Yes"] <- TRUE
archery_wide_long$experienced[archery_wide_long$experienced == "No"] <- FALSE

archery_wide_long


```

```{r}
#print first 10 outputs
print(n=10,archery_wide_long)
```





# Q4. Identifying data types

   name = It is a "Categorical Nominal",as they are not categorized on the basis of hierarchy , making it as a nominal variable.   
   
  "experienced" = "Categorical Nominal" , as it appears to be the status of the archers ,with true and false and also its a nominal variable as it has no inherent order from all the categories. 
  
  "started" = it is a"Quantitative Continuous" as it represents continuous range of values and also the this variable holds the date of each athlete or archer started
  
  "session" = it is a "Quantitative Discrete" as this variable is countable and distinct value as it doesnt have fractions or decimals
  
  "shots" = here this variable has the number of shots taken by every archer and which tends to have countable and distinct values, so it is "Quantitative Discrete" . 
  
  "hits" = it is similar to shots as it is countable and has distinct value so it is "Quantitative Discrete"      
  
  "days_experience" = it is a "Quantitative Continuous" as this variable can take any non variable non negative real value within a continuous range.
  
  "accuracy" = it is a "Quantitative Continuous, as it represents the ratio of hits to shots along with the accuracy of every archer.

# Q5(a). Taming the data
```{r}
archery_wide_long$hits <- as.integer(archery_wide_long$hits)
archery_wide_long$shots <- as.integer(archery_wide_long$shots)


archery_wide_long
```

# Q5(b). Taming the data
`
```{r}


archery_wide_long$started = dmy(archery_wide_long$started)
archery_wide_long$experienced = as.logical(archery_wide_long$experienced)
archery_wide_long
```

```{r}
#print first 10 outputs
print(n=10,archery_wide_long)
```




# Q6. Adding two new colums to dataset
# adding days_experience column
```{r}

library(lubridate)
library(dplyr)

archery_wide_long <- mutate(archery_wide_long,
                            days_experience = as.integer(difftime(as.Date("2024-02-01"), started, units = "days")))


archery_wide_long
```


# adding accuracy column
```{r}
archery_wide_long <- mutate(archery_wide_long,
                            accuracy = hits / shots)
archery_wide_long$accuracy <- archery_wide_long$hits / archery_wide_long$shots

archery_wide_long
```

```{r}
#print first 10 outputs
print(n=10,archery_wide_long)
```




# Q7. Display the sample statistics for the numerical values in your dataset


```{r}

inspect_num(archery_wide_long)


```


#q8. Subset of dataset to contain experienced ones
```{r}
archery_wide_long <- filter(archery_wide_long, experienced == TRUE)
archery_wide_long
```


```{r}
#print first 10 outputs
print(n=10,archery_wide_long)
```




#Q9. Scatter plot of accuracy and days_experience
```{r}
ggplot(archery_wide_long, aes(x = days_experience, y = accuracy)) +
  geom_point() +
  geom_smooth() 
```
# q10.
Since there is a rise in the days_experience , its a sign of positive trend, where it implies that the archers are getting more experience and their accuracy level tends to improve. However at the curve over 750 days becaomes more stable, so to be the better archer it takes anywhere around 750 to 800 days by taking plot as the reference.




