---
title: "DATA TAMING ASSIGNMENT 1"
author: "VINEETH MARIKUNTEMATHA RAVISHARADHYA-a1896845"
date: "24/03/2024"
output:
  pdf_document:
    latex_engine: xelatex
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE)
```

## R Markdown

```{r}
library(tidyverse)
library(dplyr)
library(inspectdf)
library(ggplot2)
library(lubridate)
library(caret)
library(moments)
```

```{r cars}
# Defining my student number

student_number <- 1896845  # Replace this with your actual student number

# Calculating the my dataset number with my student number
index <- (student_number + 1) %% 3

index
# Calculating the my dataset number with my student number
filename <- paste0("C:/Users/Vineeth M R/Desktop/fina/gadget_0.csv")

filename
```



#Q1. Load the correct dataset and save it as a tibble. Output the first 10 lines of the dataset.

```{r}
# Load the dataset
data <- read.csv(filename)

# Output the first 10 lines of the dataset
head(data, 10)
```



##Q2. Add a new column of row numbers to the far left of your tibble, to make it easy to refer to the cities. Output the first 10 rows of your data.


```{r}
data = mutate(data, row_num=c(1:1001))
data

n_data = relocate(data, row_num, .before = name)
# Output the first 10 lines of the dataset
head(n_data,10)
```


## Q3.3. Using dot points, identify what types of variables we now have in our data set, i.e., “Quantitative Discrete”,“Quantitative Continuous”, “Categorical Nominal”, “Categorical Ordinal”. (Don’t just describe what datatype they are in the tibble — you need to think about the type of variable in the context of the meaning of the data.) Make sure you provide some justification for your choice of variable types.

#solution:


 row_num : “Quantitative Discrete” 
 name : “Categorical Nominal”
 population : “Quantitative Discrete”
 advertising : “Quantitative Continuous” 
 sales : “Quantitative Discrete”


## 4. Now it’s time to clean and tame our data.• Clean the data by fixing any missing or erroneous data.• Make the dataset conform to the Tame Data conventions in Module 2 (page 3).(Note that you will probably have to perform cleaning and taming iteratively, meaning that you will probably want to do some cleaning, then some taming, and then realise that more cleaning is needed, then more taming,etc... Pay attention to the warnings and messages that R gives you!)


```{r}
inspect_na(n_data)


x = 1 


for (i in 1:nrow(n_data)){
    if (is.na(n_data$name[i])){
      n_data$name[i] <- paste("noname_",x)
      x <- x+1
  } 
}

n_data
inspect_na(n_data)



for (i in 1:nrow(n_data)){
  if (is.na(n_data$population[i])
      |is.na(n_data$advertising[i])|is.na(n_data$sales[i]))
    {
      n_data <- n_data[-i, ]
  } 
}

n_data
inspect_na(n_data)




duplicates <- filter(n_data, duplicated(n_data$name, fromLast = TRUE))
duplicates

# finding duplicating if any 

n_data <- n_data[-duplicates$row_num,]

n_data


duplicates2 <- filter(n_data, duplicated(n_data$name, fromLast = TRUE))
duplicates2 



n_data$advertising <- str_replace(n_data$advertising,"\\$","")
n_data$advertising <- str_replace_all(n_data$advertising,",","")
n_data$advertising <- as.numeric(n_data$advertising)
n_data$advertising <- abs(n_data$advertising)

# and getting output for the first 10 lines of the dataset of advertising column
head(n_data$advertising,10)


# froming to positive values. 
# and getting output for the first 10 lines of the dataset
head(n_data,10)

n_data$sales <- abs(n_data$sales)
n_data$population <- str_replace(n_data$population, "two hundred and fifty-seven thousand, three hundred and thirty-three","257333")

n_data$population <- as.numeric(n_data$population)
n_data$population <- abs(n_data$population)




for (i in 1:nrow(n_data)){
  if (is.na(n_data$population[i]) | is.na(n_data$advertising[i]) | is.na(n_data$sales[i])) {
    next  
  } 
  else if ((n_data$population[i]<10000) | (n_data$advertising[i]<20000) | (n_data$sales[i]<100))
  {
    n_data <- n_data[-i, ]
  } 
}

view(n_data)

for (i in 1:nrow(n_data)){
  if (is.na(n_data$population[i]) | is.na(n_data$advertising[i]) | is.na(n_data$sales[i])) {
    next  
  } 
  else if ((n_data$population[i]>10000000) | (n_data$advertising[i]>10000000) | (n_data$sales[i]>1000000))
  {
    n_data <- n_data[-i, ]
  } 
}


round_data <- function(x) {
  ifelse (x >= 1, round(x, 2), signif(x, 3))
  }

n_data$population <- round_data(n_data$population)
n_data$advertising <- round_data(n_data$advertising)
n_data$sales <- round_data(n_data$sales)
# getting output for the first 10 lines of the dataset
head(n_data,10)
```

## 5. Create new variables in your tibble, representing the:• percentage of a city’s population who bought the gadget (call the variable sales pct)• advertising expenditure per person in a city (call the variable adv exp pp)Output the first 10 rows of your data. Also, describe what type of variables these are (“Quantitative Discrete”,“Quantitative Continuous”, “Categorical Nominal”, “Categorical Ordinal”).


```{r}
n_data <- n_data %>%
  mutate(sales_pct = sales / population * 100,
         adv_exp_pp = advertising / population)

n_data$sales_pct <- round_data(n_data$sales_pct)
n_data$adv_exp_pp <- round_data(n_data$adv_exp_pp)

n_data
head(n_data,10)
```

## 6. Making sure you set the seed correctly (according to the Deliverable Specification), choose a random sample of 700 of the cities. Output the first 10 lines of your new dataset.Use this sample data set for the rest of the assignment.

```{r}
set.seed(1896845) 
n_data <- n_data %>%
  sample_n(700)
head(n_data, 10)
```


## Q7. Use inspect num to produce summary statistics for all the numerical variables in your new dataset.

```{r}
summary(n_data)

head(n_data,10)
```

## Q8. Produce a scatterplot of the two new columns sales pct and adv exp pp, with the explanatory variable on the horizontal axis and the response variable on the vertical axis. Include a straight line of best fit on your plot. Does it look like there is a linear relationship between the two variables? (Provide some reasons for your answer.)



```{r}
ggplot(n_data, aes(x = adv_exp_pp, y = sales_pct)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

## Q9. Plot a histogram of sales pct and calculate the skewness. Does the data look like a standard normal distribution? (Provide some reasons for your answer.)• (Note that to fit the linear model, we don’t really need the histogram to be roughly like a normal distribution,but it’s another interesting piece of data that is often worth checking for any glaring problems.)





```{r}
#Q9

ggplot(n_data, aes(x = sales_pct)) +
  geom_histogram() +
  stat_function(fun = dnorm, args = list(mean = mean(n_data$sales_pct), sd = sd(n_data$sales_pct)), color = "red") 
```


## Q10. We would like to fit a linear model to this data, and so we will first apply a Box-Cox transformation to the response variable.(a) Use BoxCoxTrans to obtain an estimate of λ. What is the estimate?(b) Apply the transformation to create a new column in your dataset.Output the first 10 lines of your dataset.





```{r}


# Applying Box-Cox transformation
Boooo <- BoxCoxTrans(y = n_data$sales_pct, x = n_data$adv_exp_pp)


Boooo

```


```{r}
n_data <- mutate(n_data,boox_sales_pct = round_data(predict(Boooo,n_data$sales_pct)))



head(n_data,10)


```

## Q11. Produce a scatterplot of the transformed data (with a line of best fit), as well as a histogram and the skewness.Write 2–3 sentences about this output.




```{r}
```
```{r}
library(moments)
ggplot(n_data,aes(adv_exp_pp,boox_sales_pct)) + 
  geom_point() + 
  geom_smooth()
library(moments)
ggplot(n_data, aes(boox_sales_pct)) + geom_histogram()

skewness(n_data$boox_sales_pct)

```

The scatter plot shows us that the data points are not linearly aligned close to the best fit line.






## Q12.12. (a) Write down the general equation of a linear model for this transformed data (with appropriate coefficients).
## Make sure you define any variables you introduce. (Hint: this equation should include the error
## terms.)
## (b) Also write down the formula for the line of best fit (with standard notation for the coefficients).
## (c) Now build a linear model in R, and use the output to find estimates for the model coefficients. Write
##  down the correct formula with these coefficients.

Solution: (a) The  equation of a linear model for this transformed data can be given as follows:
            Y = β0 + β1*X + ε
 
where y is a dependent variable and x is a independent variable

(b) Ŷ = β̂0 + β̂1*X
     where  β̂ is predicted value of dependent variable and  β̂1* is the estimated coefficient of the model predicted.

```{r}

##(c)

# Using box coc transformed data to lm model
mm_model <- lm(boox_sales_pct ~ adv_exp_pp, data = n_data)

summary(mm_model)


coefficients <- coef(mm_model)
coefficients

```


##Q13. Using the material in Module 6 (p. 10–13), check if our model satisfies the 4 assumptions for a linear model.You will need to write some text explaning your conclusions here. Make sure you identify at least one possibleproblem with the Independence assumption.• (Note that we are going to use a linear model regardless of any problems that you find in the assumptions,but it is always good to highlight any shortcomings of the model so the client knows about them.)

## Solution:

(a) Linearity: 


```{r}
plot(mm_model, which = 1)
```
    seeing the above graph it has a small curvature.


(b) Constant variance :

```{r}
plot(mm_model, which = 3)
```

  The red line is moving upwards slightly as the fitted values increase.

(c) Normality: This is the normal QQ plot of the residuals.


```{r}
plot(mm_model, which = 2)
```




4. Independence: This type of assumption requires the residuals to be independent of each other.







## Q14. Use your model to predict the percentage of a city’s population that will buy a Gadget 2® for each of the 3 advertising expenditure scenarios. Don’t forget the client wants an interval as well. (Hint: you will need to transform your predictions back into the scale of the original variables.)


```{r}
#taking values from the background as mentioned in the handout
exp_data <- c(0.05, 3.14, 6.00)


pred <- predict(mm_model, newdata = data.frame(adv_exp_pp = exp_data), interval = "prediction", level = 0.90)

pred

pred <- as.data.frame(pred)
pred$lower <- (pred$lwr)^2
pred$estimate <- (pred$fit)^2
pred$upper <- (pred$upr)^2


pred <- pred[, c("estimate", "lower", "upper")]


print(pred)
```
```{r}


```




## Q15.Write a few sentences to interpret your model results for the company. Make sure you highlight any predictions that are clearly erroneous, and give some explanation of why that might be.
Answer:

From the model it clearly explains the situations in three ratio i.e
low scenario: where the model predicts upto 8.642389	as lower and 0.3868563	as upper with an estimation of 3.171555	percentage.
medium scenario: where the model predicts upto 48.110002	as lower and 85.2932294	as upper with an estimation of 65.379925		percentage.
upper scenario: where the model predicts upto 257.779923	as lower and 337.8450690	as upper with an estimation of 296.461048	percentage.
























